---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GroupMeanSummary

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable) <!-- credits: taken from https://github.com/vincenzocoia/powers/blob/master/README.md -->
<!-- badges: end -->

This `R` package provides a **convenient function to calculate the arithmetic mean**. Further, the user can choose to group the data at any single or multiple levels to calculate the mean over those groupings. Moreover, for convenience, the user can select data grouping via column index(es) or column name(s).

## Installation

You can install the development version of GroupMeanSummary from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-hs235", ref = "1.0.0")
```

## Example

An example to demonstrate usage:

```{r example}
suppressPackageStartupMessages(library(GroupMeanSummary))
suppressPackageStartupMessages(library(tidyverse))

## Creating sample data
(sampleData <- data.frame(Name = c("Kelly", "Harsh", "Brad", "Kelly", "Brad"),
                 TransactionCity = c("Burnaby", "Vancouver", "Richmond", "Vancouver", "Burnaby"),
                 TransactionCost = c(100, 50, 80, 100, 40),
                 ItemsPurchased = c(4,1,4,6,2)
                 ))

## Summarizing the mean of transaction cost and items purchased per person
summarize_by_group_mean(sampleData, c(2,1))
```

## Contributers
[@Harsh](https://github.com/hs235)
